%-------------------------
% Resume in Latex
% Author : Aras Gungore
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Seher Khan} \\ \vspace{3pt}
    \small
    \faMapMarker \hspace{.5pt} Dallas\textendash Fort Worth Area, TX
    $|$
    \faMobile \hspace{.5pt} \href{tel:12132742015}{213 274 2015}
    $|$
    \faAt \hspace{.5pt} \href{mailto:seher.khan@alumni.usc.edu}{seher.khan@alumni.usc.edu}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://linkedin.com/in/khanseher}{linkedin.com/in/khanseher}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/seherkhan}{github.com/seherkhan}
\end{center}



%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    
    \resumeEducationHeading
      {University of Southern California}{Los Angeles, CA}
      {M.S. in Data Informatics; \textbf{GPA: 3.67/4.00}}{Aug 2018 \textbf{--} May 2020}
      {Coursework: Algorithms, Knowledge Graphs, Machine Learning, Probability, Information Visualization}{}
        % (Optional bullets for USC)

    \resumeEducationHeading
      {Institute of Business Administration (IBA)}{Karachi, Pakistan}
      {B.S. in Economics and Mathematics; \textbf{GPA: 3.72/4.00}}{Sep 2012 \textbf{--} Jun 2016}
      {Coursework: Programming, Econometrics, Operations Research, Stochastic Processes, Game Theory, Finance}{Research Assistant: Studied the energy sector for ``The Economy of Modern Sindh'' (Govt. of Sindh, 2016). Additional coursework: Data Structures, Artificial Intelligence, Software Engineering, Object\textendash Oriented Programming (IBA, MS CS Spring 2017, GPA 4.0/4.0)}
    
  \resumeSubHeadingListEnd



%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        
        \textbf{Languages:}{ Java, JavaScript, Python} \\ \vspace{3pt}
        
        \textbf{Frameworks:}{ React, Redux, JAX\textendash RS, Spring MVC} \\ \vspace{3pt}
        
        \textbf{AWS Cloud services:}{ DynamoDB, S3, Lambda, Step Functions, EC2, CloudWatch, CloudFormation with CDK} \\ \vspace{3pt}
        
    }}
  \resumeSubHeadingListEnd



%----------- EXPERIENCE -----------

\section{Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Amazon.com Services Inc.}{Detroit, MI}
      {Software Development Engineer II (3 years); Software Development Engineer I (2 years)}{Jul 2020 \textbf{--} Jul 2025}
        \resumeItemListStart
            \resumeItem{Designed and led implementation of foundational features such as identity verification and ``Contact Us'' on \href{https://solutionproviderportal.amazon.com}{solutionproviderportal.amazon.com}, serving $\sim$500K developers globally. Revamped RBAC privilege assignment to prevent loopholes and unexpected forbidden errors.}
            \resumeItem{Iteratively designed and implemented web apps (React.js and JSP via Spring MVC) and the microservices behind them (JAX\textendash RS and Spring Framework). Deployed services on EC2, implemented serverless components using AWS Lambda and Step Functions, and maintained CI/CD pipelines for automated deployment.}
            \resumeItem{Resolved data integrity issues by improving data table structure, extrapolating and backfilling missing data in bulk, and adding alarms for incomplete updates where atomic operations were not feasible.}
            \resumeItem{Designed and led the implementation of limits on the number of authorizations for unpublished apps to encourage rigorous vetting and discourage insecure usage.}
            \resumeItem{Migrated an external\textendash facing API from AWS Lambda to a new JAX\textendash RS service and introduced an in\textendash memory cache, reducing average request latency by 85\% (600\,ms $\rightarrow$ 92\,ms).}
            \resumeItem{Collaborated with Product, UX, Analytics, Solution Architects, and other engineering teams across time zones.}
            \resumeItem{Managed interns and mentored junior developers to support career progression.}
        \resumeItemListEnd

    \resumeSubheading
      {Engro Fertilizers}{Karachi, Pakistan}
      {Data Analyst}{Jan 2018 \textbf{--} May 2018}
        \resumeItemListStart
            \resumeItem{Analyzed and visualized agronomic data of 20K+ farmers by developing dashboards and reports (MS Excel with VBA) for an initiative to improve crop yields through personalized agronomic advice.}
        \resumeItemListEnd

    \resumeSubheading
      {The Pakistan Business Council}{Karachi, Pakistan}
      {Data Analyst}{Jul 2016 \textbf{--} Jun 2017}
        \resumeItemListStart
            \resumeItem{Analyzed Pakistan's trade with the UK, Turkey, and Chile to facilitate decision\textendash making for private\textendash sector businesses and the Government of Pakistan (approximately 6,000 copies of the reports published).}
        \resumeItemListEnd
    
  \resumeSubHeadingListEnd



%----------- PROJECTS -----------

\section{Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart
      
      \resumeProjectHeading
        {\textbf{Did the COVID\textendash 19 pandemic impact help\textendash seeking behavior for seizure management?}}{Dec 2021}
          \resumeItemListStart
            \resumeItem{Google Trends study (2nd author; Epilepsy \& Behavior). Collected, cleaned, analyzed, and visualized data; wrote methodology and results sections. \textit{Tools: Python, scikit\textendash learn, NumPy, pandas}}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{Charity Matching (Data Mining)}}{Spring 2019}
          \resumeItemListStart
            \resumeItem{Implemented collaborative filtering algorithms to recommend projects to donors of DonorsChoose.org. \textit{Tools: Apache Spark, Python}}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{Make My Playlist (Machine Learning)}}{Fall 2018}
          \resumeItemListStart
            \resumeItem{Processed features of 50K songs and trained classifiers to generate playlists given seed songs. \textit{Tools: Python, scikit\textendash learn, NumPy, pandas, Keras}}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{Imger (Data Management)}}{Fall 2018}
          \resumeItemListStart
            \resumeItem{Developed an Android app to manage phone images by extracting and editing image metadata. \textit{Tools: Android, Firebase Realtime Database and Storage}}
          \resumeItemListEnd
      
    \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
